%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Test Engineer} % Job title
    {Núcleo de Excelência em Tecnologias Sociais (NEES)} % Organization
    {Remote, Brasil} % Location
    {Jul. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Elaboration and execution of test scenarios;
        \item API testing using Karate, Postman and RestAssured;
        \item Exploratory testing;
        \item Web test automation using Selenium;
        \item Mobile test automation using Appium;
        \item Test and bug management and administration via ClickUp, Confluence and Jira;
        \item Development and extraction of reports for project and service quality metrics;
        \item Test monitoring using Testkube;
        \item Used tools: Testkube, Jira, Confluence, JMeter, K6, Postman, RestAssured, Grafana, Prometheus, GCP, Postman, and Appium.
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Teacher Assistant} % Job title
    {Universidade de São Paulo, USP} % Organization
    {São Carlos, Brasil} % Location
    {Fev. 2016 - Dez. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Produce and teach content for undergraduate courses.}
        \item {Courses: Software Testing and Inspection, Object Oriented Programming, Introduction to Computer Science, Software Engineering.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Supervisor Professor} % Job title
    {Universidade Virtual do Estado de São Paulo, UNIVESP} % Organization
    {São Paulo, Brasil} % Location
    {Jun. 2016 - Out. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Monitor the virtual student activities according to the course schedule, guiding the teaching mediators in the publications in the forums and other activities.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Information Technology Advisor} % Job title
    {Conselho Regional de Administração do Piauí, CRA-PI} % Organization
    {Teresina, Brasil} % Location
    {Jun. 2016 - Out. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {System development for process control; Build scripts to automate reporting; Monitoring and supervision tech interns; Built the institution's network infrastructure; Support and training to employees.}
        \item {Most used techs: Java, Python, MySQL, JEE, JSF, JPA, Ireport, JasperReporps.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Information Technology Intern} % Job title
    {Tribunal Regional Eleitoral do Piauí, TRE-PI} % Organization
    {Teresina, Brasil} % Location
    {Jul. 2011 - Jan. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Complementary system development for support reporting of project control tool Redmine; Maintenance of the institution Spending Control System.}
        \item {Most used techs: Java, JSF, Primefaces, JPA, Hibernate, JDBC, Ireport, JasperReporps.}
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Information Technology Intern} % Job title
    {Conselho Regional de Administração do Piauí, CRA-PI} % Organization
    {Teresina, Brasil} % Location
    {Fev. 2010 - Fev. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Operation of internal control systems; Support staff; Computer Maintenance; Backup routine control.}
        \item {Most used techs: Java, Python, MySQL}
      \end{cvitems}
    }

%---------------------------------------------------------


%---------------------------------------------------------
\end{cventries}
