%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications (Chronological Order)}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\cvsubsection{Refereed Journal Articles}

\begin{cvhonors}
%---------------------------------------------------------
  \cvhonor
    {ACM Surveys \faLeanpub} % revenue
    {JÚNIOR, MISAEL C. ; AMALFITANO, DOMENICO ; GARCÉS, LINA ; FASOLINO, ANNA RITA ; \textbf{ANDRADE, STEVÃO A.} ; DELAMARO, MÁRCIO . \textit{Dynamic Testing Techniques of Non-Functional Requirements in Mobile Apps: A Systematic Mapping Study}. ACM COMPUTING SURVEYS, v. 1, p. 3507903, 2022.} % authors
    {\href{http://dx.doi.org/10.1145/3507903}{doi}} % link
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {REIC \faLeanpub} % revenue
    {BRITO, R. O. ; \textbf{ANDRADE, STEVAO A.} ; DELMARO, M. E. . \textit{Uma Avaliação de técnicas e Critérios de Teste de Software para a Linguagem de Programação Python}. REVISTA ELETRÔNICA DE INICIAÇÃO CIENTÍFICA, v. 20, p. 1-16, 2022.} % authors
    {\href{https://sol.sbc.org.br/journals/index.php/reic/article/view/1804}{doi}} % link
    {2022} % Date(s)
    
%---------------------------------------------------------    
  \cvhonor
    {IJSEKE \faLeanpub} % revenue
    {DELAMARO, MÁRCIO E. ; \textbf{ANDRADE, STEVÃO A.} ; DE SOUZA, SIMONE R. S. ; DE SOUZA, PAULO S. L. . \textit{Parallel Execution of Programs as a Support for Mutation Testing: A Replication Study}. INTERNATIONAL JOURNAL OF SOFTWARE ENGINEERING AND KNOWLEDGE ENGINEERING, v. 31, p. 337-380, 2021.} % authors
    {\href{http://dx.doi.org/10.1142/S0218194021500121}{doi}} % link
    {2021} % Date(s)    
    
%---------------------------------------------------------
  \cvhonor
    {CI \faLeanpub} % revenue
    {\textbf{ANDRADE, STEVÃO A.}; L. S. NUNES, FATIMA ; E. DELAMARO, MARCIO . \textit{A fault-based testing approach for VR applications}. Comunicações em Informática, v. 3, p. 1-4, 2019.} % authors
    {\href{http://dx.doi.org/10.22478/ufpb.2595-0622.2019v3n2.49451}{doi}} % link
    {2019} % Date(s)    

%---------------------------------------------------------
\end{cvhonors}



\cvsubsection{Book Chapters}

\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {\faBook} % revenue
    {OLIVEIRA, R. A. P. ; SOUZA, F. C. M. ; \textbf{ANDRADE, S. A.} ; MACIEL, A. C. ; FERRARI, F. C. ; DELAMARO, M. . \textit{Ferramentas de Teste de Mutação}. In: Jose Maldonado, Marcio Delamaro, Auri Marcelo Rizzo Vincenzi. (Org.). Automatização de teste de software com ferramentas de software livre. 1ed.: Elsevier Brasil, 2018, v. , p. 1-256.} % authors
    {\href{https://avvts.net.br/livro-ats/05-Mutacao/cap-05.html}{doi}} % link
    {2018} % Date(s)

%---------------------------------------------------------    
  \cvhonor
    {\faBook} % revenue
    {Souza, Francisco Carlos ; Santos, Alinne ; \textbf{Andrade, Stevão} ; Durelli, Rafael ; Durelli, Vinicius ; Oliveira, Rafael . \textit{Automating Search Strings for Secondary Studies}. Advances in Intelligent Systems and Computing. 1ed.: Springer International Publishing, 2018, v. , p. 839-848.} % authors
    {\href{http://dx.doi.org/10.1007/978-3-319-54978-1_104}{doi}} % link
    {2018} % Date(s)
    
%---------------------------------------------------------
  \cvhonor
    {\faBook} % revenue
    {COSTA JUNIOR, M. ; \textbf{ANDRADE, S. A.} ; DELAMARO, Márcio Eduardo . \textit{Automatização de teste de software com ênfase em teste de unidade}. In: Universidade Federal do Piauí. (Org.). II Escola Regional de Informática do Piauí: livro texto dos minicursos. 1ed.Teresina: Sociedade Brasileira de Computação, 2016, v. 1, p. 121-143.} % authors
    {\href{10.13140/RG.2.2.36132.68485}{doi}} % link
    {2016} % Date(s)

%---------------------------------------------------------
\end{cvhonors}


\cvsubsection{Refereed Conference Papers (Research Track)}

\begin{cvhonors}

  \cvhonor
    {SAST \faFileTextO} % revenue
    {SANTOS, SEBASTIÃO H. N. ; DA SILVEIRA, BEATRIZ NOGUEIRA CARVALHO ; \textbf{ANDRADE, STEVÃO A.} ; DELAMARO, MÁRCIO ; SOUZA, SIMONE R. S. . \textit{An Experimental Study on Applying Metamorphic Testing in Machine Learning Applications}. In: SAST 20: 5th Brazilian Symposium on Systematic and Automated Software Testing, 2020, Natal Brazil. Proceedings of the 5th Brazilian Symposium on Systematic and Automated Software Testing, 2020. p. 98.} % authors
    {\href{http://dx.doi.org/10.13140/RG.2.2.36132.68485}{doi}} % link
    {2020} % Date(s)

%---------------------------------------------------------    
  \cvhonor
    {SVR \faFileTextO} % revenue
    {\textbf{ANDRADE, STEVAO A.}; QUEVEDO, ALVARO JOFFRE U. ; NUNES, FATIMA L. S. ; DELAMARO, MARCIO E. . Understanding VR Software Testing Needs from Stakeholders' Points of View. In: 2020 22nd Symposium on Virtual and Augmented Reality (SVR), 2020, Porto de Galinhas. 2020 22nd Symposium on Virtual and Augmented Reality (SVR), 2020. p. 57.} % authors
    {\href{http://dx.doi.org/10.1145/3425174.3425226}{doi}} % link
    {2020} % Date(s)
    
%---------------------------------------------------------    
  \cvhonor
    {MET \faFileTextO} % revenue
    {\textbf{ALVES DE ANDRADE, STEVAO}; SANTOS, ITALO ; BRITO JUNIOR, CLAUDINEI ; JUNIOR, MISAEL ; R.S. DE SOUZA, SIMONE ; E. DELAMARO, MARCIO . \textit{On Applying Metamorphic Testing: An Empirical Study on Academic Search Engines}. In: 2019 IEEE/ACM 4th International Workshop on Metamorphic Testing (MET), 2019, Montreal. 2019 IEEE/ACM 4th International Workshop on Metamorphic Testing (MET), 2019. p. 9.} % authors
    {\href{http://dx.doi.org/10.1109/SVR51698.2020.00024}{doi}} % link
    {2019} % Date(s)
    
%---------------------------------------------------------    
  \cvhonor
    {SAST \faFileTextO} % revenue
    {\textbf{ANDRADE, STEVÃO A.}; BRITO, CLAUDINEI ; JÚNIOR, MISAEL ; MARCIEL, ANA CLAUDIA ; ABDALLA, GABRIEL ; DELAMARO, MÁRCIO E. . \textit{Analyzing the effectiveness of One-Op Mutation against the minimal set of mutants}. In: the IV Brazilian Symposium, 2019, Salvador. Proceedings of the IV Brazilian Symposium on Systematic and Automated Software Testing - SAST 2019, 2019. p. 22.} % authors
    {\href{http://dx.doi.org/10.1145/3356317.3356321}{doi}} % link
    {2019} % Date(s)
    
%---------------------------------------------------------    
  \cvhonor
    {SBES \faFileTextO} % revenue
    {DE ANDRADE, STEVÃO ALVES; DE OLIVEIRA NEVES, VÂNIA ; DELAMARO, MÁRCIO EDUARDO . \textit{Software Testing Education}. In: the XXXIII Brazilian Symposium, 2019, Salvador. Proceedings of the XXXIII Brazilian Symposium on Software Engineering - SBES 2019, 2019. p. 47.} % authors
    {\href{http://dx.doi.org/10.1145/3350768.3353903}{doi}} % link
    {2019} % Date(s)
    
%---------------------------------------------------------    
  \cvhonor
    {FIE \faFileTextO} % revenue
    {AVELLAR, GUSTAVO M. N. ; SILVA, ROGERIO F. DA ; SCATALON, LILIAN P. ; \textbf{ANDRADE, STEVAO A.} ; DELAMARO, MARCIO E. ; BARBOSA, ELLEN F. . \textit{Integration of Software Testing to Programming Assignments: An Experimental Study}. In: 2019 IEEE Frontiers in Education Conference (FIE), 2019, Covington. 2019 IEEE Frontiers in Education Conference (FIE), 2019. p. 1.} % authors
    {\href{http://dx.doi.org/10.1109/FIE43999.2019.9028519}{doi}} % link
    {2019} % Date(s)
    
%---------------------------------------------------------    
  \cvhonor
    {SVR \faFileTextO} % revenue
    {\textbf{ANDRADE, STEVAO A.}; NUNES, FATIMA L. S. ; DELAMARO, MARCIO E. . \textit{Towards the Systematic Testing of Virtual Reality Programs}. In: 2019 21st Symposium on Virtual and Augmented Reality (SVR), 2019, Rio de Janeiro. 2019 21st Symposium on Virtual and Augmented Reality (SVR), 2019. p. 196.} % authors
    {\href{http://dx.doi.org/10.1109/SVR.2019.00044}{doi}} % link
    {2019} % Date(s)
    



%---------------------------------------------------------
\end{cvhonors}
